\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-12-08 docs/paper/paper.tex
bla

A similar principle is conditional independence.
If two variables are generally dependent, they can still be independent given a third variable.
An example of this is when a variable $X$ has two children $Y$ and $Z$.
$Y$ and $Z$ are generally dependent, as they share a common cause or \emph{confounder} or \emph{confounder} $X$;
When $X$ does not vary, $Y$ and $Z$ lose their confoundernd they lose their dependency.
As such, $Y$ and $Z$ are independent given \{$X$\}.

@@

The independence of $X$ and $Y$ is tested given a subset of neighbours of $X$ or $Y$ (the number of neighbours decreases while edges are removed), using the fisher-test.
If such an independence is found, this subset is a separating set of $X$ and $Y$ and they are not connected.
If no such an independence is found, they are connected.
To find the minimal separating set, the subsets of neighbours are traversed in order of size; the first separating set which is found, is the minimal one.

@@

The first of these rules attempts to find and orient V-structures.
V-structures may be found for every three nodes $X$, $Y$ and $Z$ for which $X \sline Z$, $Y \sline Z$ and in which $X$ and $Y$ are (possibly conditially) independent.
As $X$ and $Y$ are independent, they have a separating set $S$ (if they are unconditially independent, $S$ is the empty set).
If $Z$ is not in $S$, then the only possible causal relation can be that of a v-structure, so the edges can be oriented as $X \srightarrow Z \sleftarrow Y$.

@@

>>>>

A similar principle is conditional independence.
If two variables are generally dependent, they can still be independent given a third variable.
An example of this is when a variable $X$ has two children $Y$ and $Z$.
$Y$ and $Z$ are generally dependent, as they share a common cause or \emph{confounder} or \emph{confounder} $X$;
When $X$ does not vary, $Y$ and $Z$ lose their confoundernd they lose their dependency.
As such, $Y$ and $Z$ are independent given \{$X$\}.
In real-world data, independence can be found with methods such as the Fisher-Z-test.

@@

The independence of $X$ and $Y$ is tested given a subset of neighbours of $X$ or $Y$ (the number of neighbours decreases while edges are removed), using the fisher-Z-test.
If such an independence is found, this subset is a separating set of $X$ and $Y$ and they are not connected.
If no such an independence is found, they are connected.
To find the minimal separating set, all subsets of neighbours are traversed in order of size; the first separating set which is found, is the minimal one.

@@

The first of these rules attempts to find and orient V-structures.
V-structures may be found for every three nodes $X$, $Y$ and $Z$ for which $X \sline Z$, $Y \sline Z$ and in which $X$ and $Y$ are (possibly conditially) independent.
As $X$ and $Y$ are independent, they have a separating set $S$ (if they are unconditially independent, $S$ is the empty set).
If $Z$ is not in $S$, then the only possible causal relation can be that of a V-structure, so the edges can be oriented as $X \srightarrow Z \sleftarrow Y$.

@@

%TODO: pseudocode nodig? of een verwijzing naar het boek (die pseudocode is wat onduidelijk)?

\usepackage{algorithmic}

%\begin{algorithm}[PC-algorithm]
\STATE Starting state of undirected graph G: connect all pairs of points. Set n = 0.
\WHILE{there are connected pairs $X$, $Y$ such that |Adjecencies(G,X)\{Y}| < }

\ENDWHILE
%\end{algorithm}
